Aligning species range data to better serve science and conservation

### 2016-01-25 ms_2_intro_res_disc.Rmd
commented up draft for Ben, organized the drafts folder a bit

The two datasets have notably different taxonomic (Fig. 1A) and regional (Fig. 1B,C) coverage. IUCN-mapped species focus on tropical latitudes and away from the Atlantic and Eastern Pacific compared to AquaMaps-mapped species. These differences can be mitigated by using both datasets, but the underlying methodological differences complicate such direct comparisons. _and furthermore requires resolving differences (or choosing one source over the other) for the `r format(n_spp_both, big.mark = ',')` shared species._

@@

_Predictions:  What happens when using a 0% threshold instead of a 50%?  What happens when using IUCN rather than AM?  IUCN tends to overestimate extent esp for coastal species?  More species will be included in MPAs so fewer apparent gap species.  Included range area inside MPAs will increase.  Policy implications?_

>>>>

The two datasets have notably different taxonomic (Fig. 1A) and regional (Fig. 1B,C) coverage. IUCN-mapped species focus on tropical latitudes and away from the Atlantic and Eastern Pacific compared to AquaMaps-mapped species. These differences can be mitigated by using both datasets, but the underlying methodological differences complicate such direct comparisons. <!--_and furthermore requires resolving differences (or choosing one source over the other) for the `r format(n_spp_both, big.mark = ',')` shared species._-->

@@

_Predictions: What happens when using a 0% threshold instead of a 50%? What happens when using IUCN rather than AM?_
* _IUCN tends to overestimate extent esp for coastal species?  How much of this area will fall within MPAs and how much will fall outside, proportionally? this affects protection ratio._
* _More area means more species (relatively) will be at least partially included in MPAs so fewer apparent gap species?_
* _Policy implications?  Can also tie this back to the predictions of Rondinini et al re: effects of commission/omission errors_
